What's in a name? On the automated topic naming of software maintenance activities

### 2010-03-05 icpc/icpc2010.tex
mulan citation

\subsection{Supervised learning}
While unsupervised techniques (LSI and LDA are both unsupervised) are appealing in their lack of human intervention, supervised learners have the advantage of domain knowledge. This typically results in improved results. In supervised learning, the data is divided into slices. One slice is manually annotated by the domain expert
In this paper, we employ the WEKA~\cite{weka09} and Mulan machine learning frameworks in order to test supervised learning.

@@

For supervised learning, we used a suite of supervised classifiers from WEKA~\cite{weka09}. WEKA contains a suite of machine learning tools such as support vector machines and Bayes nets. We also used the multi-labeling add-on for WEKA, Mulan\footnote{\url{http://mlkd.csd.auth.gr/multilabel.html}}. Traditional classifiers map our topics to a single class, whereas Mulan allows for a mixture of classes per topic, much like our manual classification found overlaps.

@@

We applied the Mulan library for Multi-Label learning to our dataset because we feel that topics can have more like one label, much like how a revision can have more than one topic. Multi-label learning is more than just classifying entities with more than one label. It also includes methods for determining the performance of such techniques. Consider that the problem has changed, instead of looking at the precision and recall of applying one label, we have to rank multiple labels at once. We have to check if the full subset of labels was applied and then how much of that subset was applied.

@@

\XXX{Maybe cite these} Binary Relevance (BR), Calibrated Label Ranking (CLR) and Hierarchy Of Multilabel classifiERs (HOMER), performed the best. HOMER and BR acts as a hierarchy of learners, BR is flat while HOMER tries to build a deeper hierarchy in order to build a more accurate learner. We feels these classifiers performed better because they have the best micro and macro ROC scores than the other classifiers.

>>>>

\subsection{Supervised learning}
While unsupervised techniques (LSI and LDA are both unsupervised) are appealing in their lack of human intervention, supervised learners have the advantage of domain knowledge. This typically results in improved results. In supervised learning, the data is divided into slices. One slice is manually annotated by the domain expert
In this paper, we employ the WEKA~\cite{weka09} and Mulan~\cite{mulan} machine learning frameworks in order to test supervised learning.

@@

For supervised learning, we used a suite of supervised classifiers from WEKA~\cite{weka09}. WEKA contains a suite of machine learning tools such as support vector machines and Bayes nets. We also used the multi-labeling add-on for WEKA, Mulan~\cite{mulan}\footnote{\url{http://mlkd.csd.auth.gr/multilabel.html}}. Traditional classifiers map our topics to a single class, whereas Mulan allows for a mixture of classes per topic, much like our manual classification found overlaps.

@@

We applied the Mulan~\cite{mulan} library for Multi-Label learning to our dataset because we feel that topics can have more like one label, much like how a revision can have more than one topic. Multi-label learning is more than just classifying entities with more than one label. It also includes methods for determining the performance of such techniques. Consider that the problem has changed, instead of looking at the precision and recall of applying one label, we have to rank multiple labels at once. We have to check if the full subset of labels was applied and then how much of that subset was applied.

@@

 Binary Relevance (BR), Calibrated Label Ranking (CLR) and Hierarchy Of Multilabel classifiERs (HOMER), performed the best. HOMER and BR acts as a hierarchy of learners, BR is flat while HOMER tries to build a deeper hierarchy in order to build a more accurate learner~\cite{mulan}. We feels these classifiers performed better because they have the best micro and macro ROC scores than the other classifiers.
